This is an example of article title

### 2025-10-31 paper/paper.tex
A few small adaptions in TeX

\newcommand{\term}[1]{\emph{#1}}
\newcommand{\e}{\ensuremath{\mathrm{e}}}
\newcommand{\im}{\ensuremath{\mathrm{i}}}
\newcommand{\LieGroupsVersion}{0.1.7}
%
% Define muted colors.
\definecolor{TolMutedBlue}{HTML}{332288}
\definecolor{TolMutedCyan}{HTML}{88CCEE}
\definecolor{TolMutedTeal}{HTML}{44AA99}
\definecolor{TolMutedGreen}{HTML}{117733}
\definecolor{TolMutedOlive}{HTML}{999933}
\definecolor{TolMutedSand}{HTML}{DDCC77}
\definecolor{TolMutedRose}{HTML}{CC6677}
\definecolor{TolMutedWine}{HTML}{882255}
\definecolor{TolMutedPurple}{HTML}{AA4499}
%
\hypersetup{colorlinks=true}
%
\begin{document}

@@

For all three representations, one can access the component semantically by writing \verb|g[G, :Rotation]| and \verb|g[G, :Translation]|, which works independent of the representation used. This allows to implement algorithgms wotking on \(\mathrm{SE}(n)\) indepentently of the chosen representation.

@@

The presented method was applied to a case with two static charges: \SI{1e-6}{C} at position (\SI{-1}{m}, \SI{0}{m}) and \SI{-1e-6}{C} at position (\SI{1}{m}, \SI{0}{m}).
A rod of length \SI{0.67}{m} with charge density \SI{1e-6}{C/m} and mass \SI{1}{kg} started from three different initial states:
\begin{enumerate}
    \item position (\SI{0}{m}, \SI{-1.5}{m}), angle \SI{0.1}{rad}, velocity (\SI{0}{m/s}, \SI{0}{m/s}), angular velocity \SI{0}{rad/s},
    \item position (\SI{-0.2}{m}, \SI{1}{m}), angle \SI{0.2}{rad}, velocity (\SI{-0.12}{m/s}, \SI{-0.15}{m/s}), angular velocity \SI{0}{rad/s},
    \item position (\SI{-0.5}{m}, \SI{-0.5}{m}), angle \SI{0.6}{rad}, velocity (\SI{-0.04}{m/s}, \SI{0.12}{m/s}), angular velocity \SI{0}{rad/s}.
\end{enumerate}
The trajectories obtained in a simulation with time step \SI{0.001}{s} are presented in Figure~\ref{fig:Heun}.
Simulation times between \SI{30}{s} and \SI{135}{s} were chosen to have the rod remain relatively close to point charges.
Position and orientation of the rod is indicated at 20 equally spaced times, along with a densely sampled trajectory of the center of the rod.

For more advanced methods of solving differential equations on Manifolds and Lie groups in Julia, see
\verb|ManifoldDiffEq.jl|.\footnote{see \href{https://juliamanifolds.github.io/ManifoldDiffEq.jl/stable/}{juliamanifolds.github.io/ManifoldDiffEq.jl/stable/}.}

 \balance
\input{bib.tex}
\end{document}

>>>>

\newcommand{\term}[1]{\emph{#1}}
\newcommand{\e}{\ensuremath{\mathrm{e}}}
\newcommand{\im}{\ensuremath{\mathrm{i}}}
\newcommand{\LieGroupsVersion}{0.1.8}
%
% Define muted colors.
\definecolor{TolMutedBlue}{HTML}{332288}
\definecolor{TolMutedCyan}{HTML}{88CCEE}
\definecolor{TolMutedTeal}{HTML}{44AA99}
\definecolor{TolMutedGreen}{HTML}{117733}
\definecolor{TolMutedOlive}{HTML}{999933}
\definecolor{TolMutedSand}{HTML}{DDCC77}
\definecolor{TolMutedRose}{HTML}{CC6677}
\definecolor{TolMutedWine}{HTML}{882255}
\definecolor{TolMutedPurple}{HTML}{AA4499}
%
\hypersetup{colorlinks=true}
%
\begin{document}

@@

For all three representations, one can access the component semantically by writing \verb|g[G, :Rotation]| and \verb|g[G, :Translation]|, which works independent of the representation used.

@@

The presented method was applied to a case with two static charges: \SI{1e-6}{C} at position (\SI{-1}{m}, \SI{0}{m}) and \SI{-1e-6}{C} at position (\SI{1}{m}, \SI{0}{m}).
A rod of length \SI{0.67}{m} with charge density \SI{1e-6}{C/m} and mass \SI{1}{kg} started from three different initial states:
\begin{enumerate}
    \item position (\SI{0}{m}, \SI{-1.5}{m}), angle \SI{0.1}{rad}, velocity (\SI{0}{m/s}, \SI{0}{m/s}), angular velocity \SI{0}{rad/s},
    \item position (\SI{-0.2}{m}, \SI{1}{m}), angle \SI{0.2}{rad}, velocity (\SI{-0.12}{m/s}, \SI{-0.15}{m/s}), angular velocity \SI{0}{rad/s},
    \item position (\SI{-0.5}{m}, \SI{-0.5}{m}), angle \SI{0.6}{rad}, velocity (\SI{-0.04}{m/s}, \SI{0.12}{m/s}), angular velocity \SI{0}{rad/s}.
\end{enumerate}
The trajectories obtained in a simulation with time step \SI{0.001}{s} are presented in Figure~\ref{fig:Heun}.
Simulation times between \SI{30}{s} and \SI{135}{s} were chosen to have the rod remain relatively close to point charges.
Position and orientation of the rod is indicated at 20 equally spaced times, along with a densely sampled trajectory of the center of the rod.
\\
For more advanced methods of solving differential equations on Manifolds and Lie groups in Julia, see
\verb|ManifoldDiffEq.jl|.\footnote{see \href{https://juliamanifolds.github.io/ManifoldDiffEq.jl/stable/}{juliamanifolds.github.io/ManifoldDiffEq.jl/stable/}.}

%\balance
\newpage
\input{bib.tex}
\end{document}
